Information Distribution Depends on Language-Specific Features

### 2019-01-30 cogsci/position-info.Rmd
fixing switchboard

```{r, libraries}
library(png)
library(grid)
library(tidyverse)
library(xtable)
```

@@

sb_tokens <- read_feather("../switchboard/switchboard.feather") %>%
  mutate(length = str_count(value, " ") + 1) %>%
  mutate(utterance_id = 1:n()) %>%
  unnest_tokens(word, value) %>%
  group_by(utterance_id) %>%
  mutate(word_order = 1:n())

>>>>

```{r, libraries}
library(png)
library(grid)
library(tidyverse)
library(xtable)
library(tidytext)
library(tidyboot)
library(entropy)
```

@@

sb_tokens <- read_feather("../switchboard/switchboard.feather") %>%
  mutate(length = str_count(value, pattern = " +") + 1) %>% 
  mutate(utterance_id = 1:n()) %>%
  unnest_tokens(word, value, token = stringr::str_split, pattern = " +") %>%
  group_by(utterance_id) %>%
  mutate(word_order = 1:n())
